---
title: "M2-Project"
author: "Mathias Flinta"
date: "21/10/2019"
output:
  html_document: 
    toc: TRUE
    toc_float: TRUE
    df_print: paged
    code_folding: hide
    number_sections: TRUE
---

# Introduction and set-up

This project is made to be read in html, so open the html file in your preferred webbrowser. As standard the code is hidden in this document, but you can show all by pressing the button "Code" in the top right of the document. You can also show individual chunks of code by pressing the buttons "Code" which are placed around in the document. 

Link for google colab: 

Link for github: 

## Loading packages

First i have some personal setup in my local R-Markdown on how i want to display warnings ect. And then i load my packages. 
```{r}
### Knitr options
knitr::opts_chunk$set(warning=FALSE,
                     message=FALSE,
                     fig.align="center"
                     )

options(warn=-1) # Hides all warnings, as the knitr options only work on local R-Markdown mode. 

Sys.setenv(LANG = "en")
```

```{r}
# Packages
library(knitr) # For knitr to html
library(rmarkdown) # For formatting the document
library(tidyverse) # Standard datasciewnce toolkid (dplyr, ggplot2 et al.)
library(data.table) # for reading in data ect. 
library(magrittr) # For advanced piping (%>% et al.)
library(igraph) # For network analysis
library(tidygraph) # For tidy-style graph manipulation
library(ggraph) # For ggplot2 style graph plotting
library(Matrix) # For some matrix functionality
library(ggforce) # Awesome plotting
library(kableExtra) # Formatting for tables
library(car) # recode functions
library(tidytext) # Structure text within tidyverse
library(topicmodels) # For topic modelling
library(tm) # text mining library
library(quanteda) # for LSA (latent semantic analysis)
library(uwot) # for UMAP
library(dbscan) # for density based clustering

# I set a seed for reproduciability
set.seed(123) # Have to be set every time a rng proces is being made. 
```

## Loading and filtering data

Now we load the data. 
```{r}
data_raw <- read_csv("Datafiniti_Amazon_Consumer_Reviews_of_Amazon_Products.csv") %>% 
  select(name, reviews.rating, reviews.text, reviews.title) %>% 
  mutate(id = row_number())
```

# NLP - preperation



# Network analysis




# NLP



# Machine learning







